---
categories:  
- ""   
- ""
date: "2023-06-18"
description: according to 100 of my nearest and dearest 
draft: false
keywords: ""
slug: six 
title: Which code was cooler
---

```{r, setup, echo=FALSE}
knitr::opts_chunk$set(
  message = FALSE, 
  warning = FALSE, 
  tidy=FALSE,     # display code as typed
  size="small")   # slightly smaller font for code
options(digits = 3)

# default figure size
knitr::opts_chunk$set(
  fig.width=6.75, 
  fig.height=6.75,
  fig.align = "center")

```

```{r load-libraries, warning=FALSE, message=FALSE, echo=FALSE}

# Load ggplot2, dplyr, and all the other tidyverse packages
library(tidyverse)
library(skimr)
library(here)

```

# Polling which code sounded cooler

I went around to a sample of 100 people whom I am acquainted with in some way or another and asked them to look at my Python and R tiles and decide which code/application was their favourite. I recorded the data in excel (we all make mistakes), and will now analyze it here.

```{r poll_data, warning=FALSE}

# read in the data
poll <- read_csv(here::here("data","poll.csv"))

# count number of favourites for each code and plot bar graph 
poll %>% 
  count(Favourite) %>% 
  ggplot(aes(x = Favourite, y = n, fill=Favourite)) +
  geom_bar(stat = "identity") +

# some labels 
  labs(title = "Which programming language won?",
       x = "Favourite Code", y = "Number of people") +
  guides(fill="none")

```

There is a clear favourite here...

However, as a student of the scientific and rigorous persuasion, it is my duty to ascertain whether people in fact understood the choice they were making. I asked the same 100 people whether they in fact understood the Python code and the concept of what it was supposed to do.

```{r understood_data, warning=FALSE}

# count number of favourites for each code and plot bar graph 
poll %>% 
  group_by(Favourite,Understood_Python) %>% 
  count() %>% 
  ggplot(aes(x = Favourite, y = n, fill=Understood_Python)) +
  geom_bar(stat = "identity", position = "dodge") +

# some labels 
  labs(title = "Which programming language won?",
       subtitle = "and did people actually understand what they were voting for?",
       x = "Favourite Code", y = "Number of people", 
       fill="Understood the \nPython application?") 

```
